Exploring Disparate Data: Part 1

### 2024-11-04 A3-Pt1.Rmd
covid and world happiness

```{r cyclones_data_update_2, error=TRUE}
cyclones_data_update_2 <- cyclones_data_update_1 |>
    mutate(
        date = make_datetime(year = ObservYear,month = Month, day = Day, hour = Hour, min = Minute)
    )

@@

```{r aware_pop, error=TRUE}
# YOUR CODE HERE

@@

```{r aware_covid, error=TRUE}
# YOUR CODE HERE

@@

```{r happiness}
happiness <- read.xlsx("DataForTable2.1.xlsx") |>
    # YOUR CODE HERE

>>>>

```{r cyclones_data_update_2, error=TRUE}
cyclones_data_update_2 <- cyclones_data_update_1 |>
    mutate(
        date = make_datetime(ObservYear, Month, Day, Hour * 100 + Minute)
    )

@@

```{r aware_pop, error=TRUE}

aware_pop <- inner_join(
  aware_fixed_country_match,
  pop_data,
  by = "country"
) |> summarise(country, "total_population" = SP.POP.TOTL, aware_no, aware_alittle, aware_moderate, aware_alot, aware_refuse)

@@

```{r aware_covid, error=TRUE}
aware_covid <- inner_join(aware_pop, covid_2020_match_country) |>
  group_by(country) |>
  mutate(
    "cases_per_capita" = total_cases / total_population
  )

@@

```{r happiness}
happiness <- read.xlsx("DataForTable2.1.xlsx") |>
  clean_names() |>
  rename(
    "country" = country_name
  ) |>
  filter(
    !is.na(life_ladder)
  ) |>
  group_by(
    country
  ) |>
  slice_max(
    order_by = year
  )
